Title here

### 2017-01-03 portfolio/text/ms.Rmd
Edits

Managing natural resources and sustaining the livelihoods of those that depend
on their extraction is hard. These livelihoods tend to have high year-to-year
variability in income relative to other professions [@mishra2002; @sethi2012b].
In addition to economic risk, such as changes in demand or prices, individuals
dependent on natural resources are also subject to biological and environmental
variability [@smith1986]. For example, drought and flooding are a major source
of risk for agricultural food security and farmers' incomes [@gregory2005], and
catastrophic disease outbreaks and wildfires increase risk for the logging
industry [@kirilenko2007].

Individuals who rely on natural resources for income develop strategies to
reduce income variability. For example, farmers may rotate their crops to buffer
short-term climate variation and long-term environmental trends [@zentner1988].
Similarly, loggers maintain a diverse mix of tree species, age structure, and
harvest in geographical areas to buffer against disease outbreak, wildfires, and
price variation (REF). However, external forces may restrict the available
options to dampen income variability. Otherwise well-intentioned regulations may
limit how individuals diversify, or incentivize against diversification. For
example, in terrestrial agriculture, crop subsidies in the US may incentivize
some farms to specialize (e.g. dairy, grains, soybeans; @mishra2002). In other
instances, external market forces (e.g. prices or demand) may discourage the
adoption of diverse strategies and help promote specialization [@bradshaw2004].

@@

Our results across fishing strategies are in line with previous findings
[@kasperski2013, @sethi2012b, @sethi2014] at the community and vessel levels,
but our results with respect to individual year-to-year behaviour provide new
insights. Within strategies, specializing tended to be associated with
increased revenue. This could be for a number of reasons. First, specialization
can increase efficiency [@smith1986] and individual behaviour is an important
component to the efficiency of catch [@hilborn1985]. Indeed, specialization can
also increase efficiency in other natural resource industries, such as rice
production [@abdulai2000]. Second, given the availability of "cash crops",
specializing can be highly profitable. For example, when cocoa prices have been
high, cocoa farmers in Nigeria have been highly specialized on the crop
[@mustapha1999] and specializing on valuable tobacco farming can be the optimal
strategy regardless of alternative crops [@chavez2014]. In our analyses,
fishers with available sockeye salmon, a highly valuable species, benefited the
most from specializing. However, specializing can have long-term risks if
marker, biological, or environmental conditions change. For instance, U.S.
farmers specialized on wheat, corn, or soybeans were hardest hit in the early
1980s when a financial crisis hit [@ikerd1990]. Third, a lack of specialization
can happen as a consequence of non-ideal circumstances such as poor
availability of a more valuable fish stock in a given year. For example,
downward economic shocks have been associated with increased diversity for
households relying on forests for income [@debela2012].

We also found that altering species diversity tended to be associated with
increased revenue variability. There are number of reasons by annual revenue
variability might increase with changes to individual fished species diversity.
First, changes to fishing patterns will sometimes be associated with a learning
or adaptation phase as individuals become accustomed to new locations, new
gear, or new species [REF]. Secondly, changes in diversity might reflect years
in which targeted species were less available and fishers were forced to target
other species or landed more bycatch adding stochasticity to their revenue.
Most importantly, this increased variability technically reflects an inability
for our large-scale model to predict an individual's revenue in a subsequent
year. There are many reasons, often unique to an individual permit holder's
behaviour [@hilborn1985] and therefore not included in a large-scale model, that
might make that specific individual's revenue less predictable if species
diversity changes.

>>>>

Managing natural resources and sustaining the livelihoods of those that depend
on their extraction is hard. These livelihoods tend to have high annual
variability in income relative to other professions [@mishra2002; @sethi2012b].
In addition to economic risk, such as changes in demand or prices, individuals
dependent on natural resources are also subject to biological and environmental
variability [@smith1986]. For example, drought and flooding are a major source
of risk for agricultural food security and farmers' incomes [@gregory2005], and
catastrophic disease outbreaks and wildfires increase risk for the logging
industry [@kirilenko2007].

Individuals who rely on natural resources for income develop strategies to
reduce income variability. For example, farmers may rotate their crops to buffer
short-term climate variation and long-term environmental trends [@zentner1988].
Similarly, loggers maintain a diverse mix of tree species, age structure, and
harvest in geographical areas to buffer against disease outbreak, wildfires, and
price variation (REF). However, external forces may restrict the available
options to dampen income variability. Otherwise well-intentioned regulations may
limit how individuals diversify, or incentivize against diversification. For
example, in terrestrial agriculture, crop subsidies in the U.S. may incentivize
some farms to specialize (e.g. dairy, grains, soybeans; @mishra2002). In other
instances, external market forces (e.g. prices or demand) may discourage the
adoption of diverse strategies and help promote specialization [@bradshaw2004].

@@

Our results across fishing strategies are in line with previous findings at the
community and vessel levels [@kasperski2013; @sethi2012b; @sethi2014], but our
results with respect to individual year-to-year behaviour provide new insights.
Within strategies, specializing tended to be associated with increased revenue.
This could be for a number of reasons. First, specialization can increase
fishing efficiency [@smith1986]. Efficiency gains from specialization can be
seen in other natural resource sectors. For example, rice farmers in Ghana can
increase their efficiency by devoting more land and labor to rice production
compared to other crops [@abdulai2000]. Second, given the availability of "cash
crops", specializing can be highly profitable. For instance, when cocoa prices
have been high, farmers in Nigeria have been highly specialized on the crop
[@mustapha1999] and specializing on valuable tobacco farming can be the optimal
strategy regardless of alternative crops [@chavez2014]. In our analyses,
fishers with the opportunity to fish highly valuable sockeye salmon benefited
the most from specializing. However, specializing can have longterm risks if
market, biological, or environmental conditions change. For example, U.S.
farmers specialized on wheat, corn, or soybeans were hit harder than
diversified farmers in the early 1980s when a financial crisis hit
[@ikerd1990]. Third, a lack of specialization can happen as a consequence of
non-ideal circumstances such as poor availability of a more valuable fish stock
in a given year. For example, downward economic shocks have been associated
with increased diversity for households relying on forests for income
[@debela2012].

We also found that altering species diversity tended to be associated with
increased revenue variability. There are number of possible reasons for this
relationship. For instance, changes to fishing patterns will sometimes be
associated with a learning or adaptation phase as individuals become accustomed
to new locations, new gear, or new species [REF]. Additionally, changes in
diversity might reflect years in which targeted species were less available and
fishers were forced to target other species or landed more bycatch adding
stochasticity to their revenue. Most importantly, this increased variability
reflects an inability for our large-scale model to predict an individual's
revenue in a subsequent year. There are many reasons, often unique to an
individual permit holder's behaviour [@hilborn1985] and therefore not included
in our large-scale model, that might make that specific individual's revenue
less predictable if species diversity changes.
